PANCHANGE_analysis

### 2020-08-24 PANCHANGE_analysis.Rmd
disorder plot

### Summary scores
```{r descriptives gad.sum_score_cols}
gad.sum_score_numeric_table <- dat %>% 
  #    group_by(Sample) %>%
  summarise_at( 
    vars(
      "Prepan" = gad.sum_score_prepan,
      "Base" = gad.sum_score_base,
      "Retro" = gad.sum_score_retro
    ),
    .funs =
      list(
        ~mean(., na.rm = T),
        ~sd(., na.rm = T),
        ~median(., na.rm = T),
        ~min(., na.rm = T),
        ~max(., na.rm = T),
        ~skew(., na.rm = T),
        kurtosis = ~kurtosi(., na.rm = T)
      )
  )

@@

```{r smart numeric summary tables}
# reshape the table
gad.sum_score_numeric_summary_table_reshaped <- gad.sum_score_numeric_table %>% 
  gather(key, value) %>% 
  separate(key, c("variable", "measure"), sep = "_") %>%
  mutate(measure = factor(
    x = measure,
    levels =  c( # this is the order I want my columns to appear in
      "missing",
      "min",
      "max",
      "mean", 
      "median", 
      "mode",
      "sd",
      "skew",
      "kurtosis"
    ))) %>% 
  spread(measure, value) %>% 
  # we can apply a function to all variables to edit them so that they are publication ready
  rename_all(
    .funs = ~str_to_title(.)
  ) %>% 
  # or we can individually rename variables 
  rename(
    SD = Sd
  )

@@

```{r descriptives gad.diff_score_cols}
gad.numeric_table <- dat %>% 
#  group_by(dem.sex) %>%
  summarise_at( 
    vars(
      "Base - prepan" = gad.diff_score_base_prepan,
      "Base - retro" = gad.diff_score_base_retro,
      "Prepan - retro" = gad.diff_score_retro_prepan,
    ),
    .funs =
      list(
        ~mean(., na.rm = T),
        ~sd(., na.rm = T),
        ~median(., na.rm = T),
        ~min(., na.rm = T),
        ~max(., na.rm = T),
        ~skew(., na.rm = T),
        kurtosis = ~kurtosi(., na.rm = T)
      )
  )

@@

```{r smart numeric summary tables}
# reshape the table
gad.numeric_summary_table_reshaped <- gad.numeric_table %>% 
  gather(key, value) %>% 
  separate(key, c("variable", "measure"), sep = "_") %>%
  mutate(measure = factor(
    x = measure,
    levels =  c( # this is the order I want my columns to appear in
      "missing",
      "min",
      "max",
      "mean", 
      "median", 
      "mode",
      "sd",
      "skew",
      "kurtosis"
    ))) %>% 
  spread(measure, value) %>% 
  # we can apply a function to all variables to edit them so that they are publication ready
  rename_all(
    .funs = ~str_to_title(.)
    ) %>% 
  # or we can individually rename variables 
  rename(
    SD = Sd
  )

@@

```{r gad percentage plot retro_prepan}
dat.long.gad.diff %>%
  filter(Time_point != "retro_prepan") %>%
  ggplot(mapping = aes(
    x = gad.diff_score,
    y = stat(density*width),
    fill = Time_point)) +
  geom_histogram(
    binwidth = 1,
    position = position_dodge2(preserve = "single")
  ) +
  labs(
    x = "Difference GAD7 score",
    y = "Percentage of participants",
    fill = "Comparison:\nBaseline vs") +
  theme_personal +
  scale_fill_manual(values = palette, labels = c("Prepandemic", "Retrospective")) +
  facet_wrap("Disorder")
```

@@

### Summary scores
```{r descriptives phq.sum_score}
phq.sum_score_numeric_table <- dat %>% 
  #    group_by(Sample) %>%
  summarise_at( 
    vars(
      "Prepan" = phq.sum_score_prepan,
      "Base" = phq.sum_score_base,
      "Retro" = phq.sum_score_retro
    ),
    .funs =
      list(
        ~mean(., na.rm = T),
        ~sd(., na.rm = T),
        ~median(., na.rm = T),
        ~min(., na.rm = T),
        ~max(., na.rm = T),
        ~skew(., na.rm = T),
        kurtosis = ~kurtosi(., na.rm = T)
      )
  )

@@

```{r smart numeric summary tables}
# reshape the table
phq.sum_score_numeric_summary_table_reshaped <- phq.sum_score_numeric_table %>% 
  gather(key, value) %>% 
  separate(key, c("variable", "measure"), sep = "_") %>%
  mutate(measure = factor(
    x = measure,
    levels =  c( # this is the order I want my columns to appear in
      "missing",
      "min",
      "max",
      "mean", 
      "median", 
      "mode",
      "sd",
      "skew",
      "kurtosis"
    ))) %>% 
  spread(measure, value) %>% 
  # we can apply a function to all variables to edit them so that they are publication ready
  rename_all(
    .funs = ~str_to_title(.)
  ) %>% 
  # or we can individually rename variables 
  rename(
    SD = Sd
  )

@@

```{r descriptives phq.diff_score_cols}
phq.numeric_table <- dat %>% 
  #  group_by(dem.sex) %>%
  summarise_at( 
    vars(
      "Base - prepan" = phq.diff_score_base_prepan,
      "Base - retro" = phq.diff_score_base_retro,
      "Prepan - retro" = phq.diff_score_retro_prepan
    ),
    .funs =
      list(
        ~mean(., na.rm = T),
        ~sd(., na.rm = T),
        ~median(., na.rm = T),
        ~min(., na.rm = T),
        ~max(., na.rm = T),
        ~skew(., na.rm = T),
        kurtosis = ~kurtosi(., na.rm = T)
      )
  )

@@

```{r smart numeric summary tables}
# reshape the table
phq.numeric_summary_table_reshaped <- phq.numeric_table %>% 
  gather(key, value) %>% 
  separate(key, c("variable", "measure"), sep = "_") %>%
  mutate(measure = factor(
    x = measure,
    levels =  c( # this is the order I want my columns to appear in
      "missing",
      "min",
      "max",
      "mean", 
      "median", 
      "mode",
      "sd",
      "skew",
      "kurtosis"
    ))) %>% 
  spread(measure, value) %>% 
  # we can apply a function to all variables to edit them so that they are publication ready
  rename_all(
    .funs = ~str_to_title(.)
  ) %>% 
  # or we can individually rename variables 
  rename(
    SD = Sd
  )

@@

```{r phq gather to long format Time_points}
dat.long.phq.diff <- dat %>%
  gather(
    key = "Time_point_raw",
    value = "phq.diff_score",
    all_of(phq.diff_score_cols)) %>%
  select(
    ID,
    Sample,
    Gender,
    Ethnicity,
    Time_point_raw,
    phq.diff_score
  ) %>%
  mutate(Time_point = str_replace(Time_point_raw, "phq.diff_score_", "")) %>%
  select(-Time_point_raw)

@@

@@

### Split sample in improvement and worsening
```{r ocir improvment worsening stratification}
dat <- dat %>%
  mutate(ocir.change_binary_numeric =
           case_when(
             ocir.pandemic_felt_feelings_numeric == 1 ~ 1,
             ocir.pandemic_felt_feelings_numeric == 2 ~ 1,
             ocir.pandemic_felt_feelings_numeric == 3 ~ 0,
             ocir.pandemic_felt_feelings_numeric == 4 ~ 2,
             ocir.pandemic_felt_feelings_numeric == 5 ~ 2
           )
  )

@@

### Summary scores
```{r descriptives ocir.sum_score}
ocir.sum_score_numeric_table <- dat %>% 
  #    group_by(Sample) %>%
  summarise_at( 
    vars(
      "Prepan" = ocir.sum_score_prepan,
      "Base" = ocir.sum_score_base,
      "Retro" = ocir.sum_score_retro
    ),
    .funs =
      list(
        ~mean(., na.rm = T),
        ~sd(., na.rm = T),
        ~median(., na.rm = T),
        ~min(., na.rm = T),
        ~max(., na.rm = T),
        ~skew(., na.rm = T),
        kurtosis = ~kurtosi(., na.rm = T)
      )
  )

@@

```{r smart numeric summary tables}
# reshape the table
ocir.sum_score_numeric_summary_table_reshaped <- ocir.sum_score_numeric_table %>% 
  gather(key, value) %>% 
  separate(key, c("variable", "measure"), sep = "_") %>%
  mutate(measure = factor(
    x = measure,
    levels =  c( # this is the order I want my columns to appear in
      "missing",
      "min",
      "max",
      "mean", 
      "median", 
      "mode",
      "sd",
      "skew",
      "kurtosis"
    ))) %>% 
  spread(measure, value) %>% 
  # we can apply a function to all variables to edit them so that they are publication ready
  rename_all(
    .funs = ~str_to_title(.)
  ) %>% 
  # or we can individually rename variables 
  rename(
    SD = Sd
  )

@@

```{r ocir gather to long format Time_points}
dat.long.ocir.diff <- dat %>%
  gather(
    key = "Time_point_raw",
    value = "ocir.diff_score",
    all_of(ocir.diff_score_cols)) %>%
  select(
    ID,
    Sample,
    Gender,
    Ethnicity,
    Time_point_raw,
    ocir.diff_score
  ) %>%
  mutate(Time_point = str_replace(Time_point_raw, "ocir.diff_score_", "")) %>%
  select(-Time_point_raw)

@@

```{r ocir percentage plot retro_prepan}
dat.long.ocir.diff %>%
  filter(Time_point != "retro_prepan") %>%
  ggplot(mapping = aes(
    x = ocir.diff_score,
    y = stat(density*width),
    fill = Time_point)) +
  geom_histogram(
    binwidth = 1,
    position = position_dodge2(preserve = "single")
  ) +
  labs(
    x = "Difference ocir7 score",
    y = "Percentage of participants",
    fill = "Comparison:\nBaseline vs") +
  theme_personal +
  scale_fill_manual(values = palette, labels = c("Prepandemic", "Retrospective"))
```

@@

>>>>

### Summary scores
```{r descriptives gad.sum_score_cols}
gad.sum_score_numeric_table <- dat %>% 
  group_by(gad.change_binary) %>%
  summarise_at( 
    vars(
      "Prepan" = gad.sum_score_prepan,
      "Base" = gad.sum_score_base,
      "Retro" = gad.sum_score_retro
    ),
    .funs =
      list(
        ~mean(., na.rm = T),
        ~sd(., na.rm = T),
        ~median(., na.rm = T),
        ~min(., na.rm = T),
        ~max(., na.rm = T),
        ~skew(., na.rm = T),
        kurtosis = ~kurtosi(., na.rm = T)
      )
  )

@@

```{r smart numeric summary tables}
# reshape the table
gad.sum_score_numeric_summary_table_reshaped <- gad.sum_score_numeric_table %>% 
  gather(key, value, -gad.change_binary) %>% 
  separate(key, c("variable", "measure"), sep = "_") %>%
  mutate(measure = factor(
    x = measure,
    levels =  c( # this is the order I want my columns to appear in
      "missing",
      "min",
      "max",
      "mean", 
      "median", 
      "mode",
      "sd",
      "skew",
      "kurtosis"
    ))) %>% 
  spread(measure, value) %>% 
  # we can apply a function to all variables to edit them so that they are publication ready
  rename_all(
    .funs = ~str_to_title(.)
  ) %>% 
  # or we can individually rename variables 
  rename(
    Change = Gad.change_binary,
    SD = Sd
  )

@@

```{r descriptives gad.diff_score_cols}
gad.numeric_table <- dat %>% 
  group_by(gad.change_binary) %>%
  summarise_at( 
    vars(
      "Base - prepan" = gad.diff_score_base_prepan,
      "Base - retro" = gad.diff_score_base_retro,
      "Prepan - retro" = gad.diff_score_retro_prepan
    ),
    .funs =
      list(
        ~mean(., na.rm = T),
        ~sd(., na.rm = T),
        ~median(., na.rm = T),
        ~min(., na.rm = T),
        ~max(., na.rm = T),
        ~skew(., na.rm = T),
        kurtosis = ~kurtosi(., na.rm = T)
      )
  )

@@

```{r smart numeric summary tables}
# reshape the table
gad.numeric_summary_table_reshaped <- gad.numeric_table %>% 
  gather(key, value, -gad.change_binary) %>% 
  separate(key, c("variable", "measure"), sep = "_") %>%
  mutate(measure = factor(
    x = measure,
    levels =  c( # this is the order I want my columns to appear in
      "missing",
      "min",
      "max",
      "mean", 
      "median", 
      "mode",
      "sd",
      "skew",
      "kurtosis"
    ))) %>% 
  spread(measure, value) %>% 
  # we can apply a function to all variables to edit them so that they are publication ready
  rename_all(
    .funs = ~str_to_title(.)
    ) %>% 
  # or we can individually rename variables 
  rename(
    Change = Gad.change_binary,
    SD = Sd
  )

@@

```{r gad percentage plot retro_prepan, fig.height=6, fig.width=10}
dat.long.gad.diff %>%
  filter(Time_point != "retro_prepan") %>%
  ggplot(mapping = aes(
    x = gad.diff_score,
    y = stat(density*width),
    fill = Time_point)) +
  geom_histogram(
    binwidth = 1,
    position = position_dodge2(preserve = "single")
  ) +
  labs(
    x = "Difference GAD7 score",
    y = "Percentage of participants",
    fill = "Comparison:\nBaseline vs") +
  theme_personal +
  scale_fill_manual(values = palette, labels = c("Prepandemic", "Retrospective")) +
  facet_wrap("Disorder")
```

@@

### Summary scores
```{r descriptives phq.sum_score}
phq.sum_score_numeric_table <- dat %>% 
  group_by(phq.change_binary) %>%
  summarise_at( 
    vars(
      "Prepan" = phq.sum_score_prepan,
      "Base" = phq.sum_score_base,
      "Retro" = phq.sum_score_retro
    ),
    .funs =
      list(
        ~mean(., na.rm = T),
        ~sd(., na.rm = T),
        ~median(., na.rm = T),
        ~min(., na.rm = T),
        ~max(., na.rm = T),
        ~skew(., na.rm = T),
        kurtosis = ~kurtosi(., na.rm = T)
      )
  )

@@

```{r smart numeric summary tables}
# reshape the table
phq.sum_score_numeric_summary_table_reshaped <- phq.sum_score_numeric_table %>%
  gather(key, value, -phq.change_binary) %>% 
  separate(key, c("variable", "measure"), sep = "_") %>%
  mutate(measure = factor(
    x = measure,
    levels =  c( # this is the order I want my columns to appear in
      "missing",
      "min",
      "max",
      "mean", 
      "median", 
      "mode",
      "sd",
      "skew",
      "kurtosis"
    ))) %>% 
  spread(measure, value) %>% 
  # we can apply a function to all variables to edit them so that they are publication ready
  rename_all(
    .funs = ~str_to_title(.)
  ) %>% 
  # or we can individually rename variables 
  rename(
    SD = Sd
  )

@@

```{r descriptives phq.diff_score_cols}
phq.numeric_table <- dat %>% 
  group_by(phq.change_binary) %>%
  summarise_at( 
    vars(
      "Base - prepan" = phq.diff_score_base_prepan,
      "Base - retro" = phq.diff_score_base_retro,
      "Prepan - retro" = phq.diff_score_retro_prepan
    ),
    .funs =
      list(
        ~mean(., na.rm = T),
        ~sd(., na.rm = T),
        ~median(., na.rm = T),
        ~min(., na.rm = T),
        ~max(., na.rm = T),
        ~skew(., na.rm = T),
        kurtosis = ~kurtosi(., na.rm = T)
      )
  )

@@

```{r smart numeric summary tables}
# reshape the table
phq.numeric_summary_table_reshaped <- phq.numeric_table %>% 
  gather(key, value, -phq.change_binary) %>% 
  separate(key, c("variable", "measure"), sep = "_") %>%
  mutate(measure = factor(
    x = measure,
    levels =  c( # this is the order I want my columns to appear in
      "missing",
      "min",
      "max",
      "mean", 
      "median", 
      "mode",
      "sd",
      "skew",
      "kurtosis"
    ))) %>% 
  spread(measure, value) %>% 
  # we can apply a function to all variables to edit them so that they are publication ready
  rename_all(
    .funs = ~str_to_title(.)
  ) %>% 
  # or we can individually rename variables 
  rename(
    SD = Sd
  )

@@

```{r phq gather to long format Time_points}
dat.long.phq.diff <- dat %>%
  gather(
    key = "Time_point_raw",
    value = "phq.diff_score",
    all_of(phq.diff_score_cols)) %>%
  select(
    ID,
    Sample,
    Gender,
    Ethnicity,
    Disorder,
    Time_point_raw,
    phq.diff_score
  ) %>%
  mutate(Time_point = str_replace(Time_point_raw, "phq.diff_score_", "")) %>%
  select(-Time_point_raw)

@@

```{r phq percentage plot retro_prepan, fig.height=6, fig.width=10}
dat.long.phq.diff %>%
  filter(Time_point != "retro_prepan") %>%
  ggplot(mapping = aes(
    x = phq.diff_score,
    y = stat(density*width),
    fill = Time_point)) +
  geom_histogram(
    binwidth = 1,
    position = position_dodge2(preserve = "single")
  ) +
  labs(
    x = "Difference PHQ9 score",
    y = "Percentage of participants",
    fill = "Comparison:\nBaseline vs") +
  theme_personal +
  scale_fill_manual(values = palette, labels = c("Prepandemic", "Retrospective")) +
  facet_wrap("Disorder")
```

@@

### Split sample in improvement and worsening
```{r ocir improvment worsening stratification}
dat <- dat %>%
  mutate(ocir.change_binary_numeric =
           case_when(
             ocir.felt_pandemic_feelings_numeric == 1 ~ 1,
             ocir.felt_pandemic_feelings_numeric == 2 ~ 1,
             ocir.felt_pandemic_feelings_numeric == 3 ~ 0,
             ocir.felt_pandemic_feelings_numeric == 4 ~ 2,
             ocir.felt_pandemic_feelings_numeric == 5 ~ 2
           )
  )

@@

### Summary scores
```{r descriptives ocir.sum_score}
ocir.sum_score_numeric_table <- dat %>% 
  group_by(ocir.change_binary) %>%
  summarise_at( 
    vars(
      "Prepan" = ocir.sum_score_prepan,
      "Base" = ocir.sum_score_base,
      "Retro" = ocir.sum_score_retro
    ),
    .funs =
      list(
        ~mean(., na.rm = T),
        ~sd(., na.rm = T),
        ~median(., na.rm = T),
        ~min(., na.rm = T),
        ~max(., na.rm = T),
        ~skew(., na.rm = T),
        kurtosis = ~kurtosi(., na.rm = T)
      )
  )

@@

```{r smart numeric summary tables}
# reshape the table
ocir.sum_score_numeric_summary_table_reshaped <- ocir.sum_score_numeric_table %>%
  filter(ocir.change_binary == "Worsening") %>%
  select(-ocir.change_binary) %>%
  gather(key, value) %>% 
  separate(key, c("variable", "measure"), sep = "_") %>%
  mutate(measure = factor(
    x = measure,
    levels =  c( # this is the order I want my columns to appear in
      "missing",
      "min",
      "max",
      "mean", 
      "median", 
      "mode",
      "sd",
      "skew",
      "kurtosis"
    ))) %>% 
  spread(measure, value) %>% 
  # we can apply a function to all variables to edit them so that they are publication ready
  rename_all(
    .funs = ~str_to_title(.)
  ) %>% 
  # or we can individually rename variables 
  rename(
    SD = Sd
  )

@@

```{r ocir gather to long format Time_points}
dat.long.ocir.diff <- dat %>%
  gather(
    key = "Time_point_raw",
    value = "ocir.diff_score",
    all_of(ocir.diff_score_cols)) %>%
  select(
    ID,
    Sample,
    Gender,
    Ethnicity,
    Disorder,
    Time_point_raw,
    ocir.diff_score
  ) %>%
  mutate(Time_point = str_replace(Time_point_raw, "ocir.diff_score_", "")) %>%
  select(-Time_point_raw)

@@

```{r ocir percentage plot retro_prepan}
dat.long.ocir.diff %>%
  filter(Time_point != "retro_prepan") %>%
  ggplot(mapping = aes(
    x = ocir.diff_score,
    y = stat(density*width),
    fill = Time_point)) +
  geom_histogram(
    binwidth = 1,
    position = position_dodge2(preserve = "single")
  ) +
  labs(
    x = "Difference OCI-R score",
    y = "Percentage of participants",
    fill = "Comparison:\nBaseline vs") +
  theme_personal +
  scale_fill_manual(values = palette, labels = c("Prepandemic", "Retrospective"))
```

@@

```{r ocir percentage plot retro_prepan, fig.height=6, fig.width=10}
dat.long.ocir.diff %>%
  filter(Time_point != "retro_prepan") %>%
  ggplot(mapping = aes(
    x = ocir.diff_score,
    y = stat(density*width),
    fill = Time_point)) +
  geom_histogram(
    binwidth = 1,
    position = position_dodge2(preserve = "single")
  ) +
  labs(
    x = "Difference OCI-R score",
    y = "Percentage of participants",
    fill = "Comparison:\nBaseline vs") +
  theme_personal +
  scale_fill_manual(values = palette, labels = c("Prepandemic", "Retrospective")) +
  facet_wrap("Disorder")
```
